---
title: "MA677_HW3"
author: "Sky Liu"
date: "3/8/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Hmisc)
```

```{r}
mu = read.table("maybe_uniform.txt")
mu<-c(mu[1,],mu[2,],mu[3,],mu[4,],mu[5,])
mu<-as.numeric(mu)
ks.test(mu, "punif")
hist(mu)

plot(1:25,mu)
```

Given the p value of KS test being 0.35, we fail to reject the null hypothsis that the data from maybe_uniform txt is uniformlly distributed.

```{r}

x<-seq(-10, 10, by=0.001)
fx <- ifelse(x > 0 & x <=0.5, 2/3,
   ifelse(x > 0.5 & x < 1,  1/2, 0))
ks.test(fx,mu)
```
From the KS test, we could see that the data does not have matched distribution with the piecewise model, with very small p value and much higher D value than the previous one. Thus, the model is not better than uniform distribution.

```{r}
ks.test(mu, "pgamma", rate = 2, shape = 1) 
```

The KS test of gamma distribution with rate = 2 and shape = 1 gives even smaller D value than uniform distribution, showing the gamma distribution is a bit better.


## Problem 2

```{r}

mn = read.table("maybe_normal.txt")
mn<-c(mn[1,],mn[2,],mn[3,],mn[4,],mn[5,])
mn<-as.numeric(mn)

n25 <- rnorm(25, 26, 4)
ks.test(mn, n25)
mean(mn)
var(mn)
hist(mn)
qqplot(1:25,mn)
```

Given the p value of KS test being 0.285, we fail to reject the null hypothsis that the data from maybe_normal txt is normally distributed.

## Problem 3

```{r}

X = read.table("maybe_same_1.txt")
X<-c(X[1,],X[2,],X[3,],X[4,],X[5,])
X<-as.numeric(X)

Y = read.table("maybe_same_2.txt")
Y<-c(Y[1,],Y[2,],Y[3,],Y[4,],Y[5,])
Y<-as.numeric(Y)
X2<-X+2

ks.test(X, Y)
ks.test(X+2, Y)

```

Given the p value of KS test between X and Y being 0.491, we fail to reject the null hypothsis that X and Y are from the same distribution.

The p value of KS test between X+2 and Y is 0.0001673, it is likely we could reject the null hypothesis that X+2 and Y are from the same distribution.

## Problem 4
```{r}
NS <- readRDS("norm_sample.Rdata")
NS <- as.data.frame(NS)
colnames(NS) <- "x"
NS_d <- ecdf(NS$x)
NS$ecdf <- NS_d(NS$x)
NS$nm <- pnorm(NS$x)
NS$D <- NS$ecdf - NS$nm
max(abs(NS$D))
ks.test(NS$x, "pnorm", 0,  1)

```

The calculated D value is 0.137, the KS test D value is 0.177. From the test, we fail to reject the null hypothesis that the normal sample data is normally distributed.

## Problem 5

### fujiquakes
```{r}
FJ <- read.table("fijiquakes.dat", header = T)
FJ_d <- ecdf(FJ$mag)
# 95% CI for F(4.9) - F(4.3)
CI<-sum((FJ$mag<=4.9) & (FJ$mag>4.3))
binconf(CI,length(FJ$mag),method="wilson",0.05)
```

### faithful
```{r}

FF <- read.table("faithful.dat", header = T, skip = 25)
f_d <- ecdf(FF$waiting)
# 90% confidence interval for mean
m <- mean(FF$waiting)
se <- sd(FF$waiting)/sqrt(length(FF$waiting))
print(paste0("90% CI for mean waiting time is [",
             round(m-1.64*se,2),", ", round(m+1.64*se,2),"]"))
# median waiting time
summary(f_d)
```